\documentclass[mathserif]{beamer}

\usepackage{parskip}

\frenchspacing

\title{Welcome to the Mackenzie Math Club}
\subtitle{The year of \textrm{\LaTeX{}}}
\author{Vincent Macri \and Samantha Unger \and Caroline Liu}
\date{2017-2018}

\usetheme{Rochester}
\usecolortheme{whale}
\beamertemplatenavigationsymbolsempty

\begin{document}
	\frame{\titlepage}
	\begin{frame}
		\frametitle{Executive team}
		\pause
		\begin{itemize}[<+->]
			\item Vincent Macri
			\item Samantha Unger
			\item Caroline Liu
		\end{itemize}
	\end{frame}
	\begin{frame}
		\frametitle{Contact us}
		\begin{center}
			\Large
			\url{mackenziemathclub.github.io/contact/}
		\end{center}
	\end{frame}
	\begin{frame}
		\frametitle{What is Math Club?}
		Math Club has been totally revamped for this year, so prepare yourself for Math Club like you've never seen!

		We meet every Monday in \alert{this} room, room 227!
	\end{frame}
	\begin{frame}
		\frametitle{What does Math Club do?}
		Every week we will introduce a new concept and teach it.
		\pause
		
		We will always have worksheets to work on instead for any students who already know the topic, or for any students who are in a lower grade and don't have the prerequisite knowledge.
		\pause

		So if you're in grade 9, we don't expect you to follow along with a lesson requiring calculus, but you can certainly try!
	\end{frame}
	\begin{frame}
		\frametitle{Guest lectures}
		We are introducing a new program to Math Club this year: guest lectures.
		\pause

		Are you really excited about something in math?
		\pause

		Want to discuss Terrence Tao's latest paper?
		\pause

		Then sign up to be a guest lecturer! We will work with you to design a lesson which you can teach at Math Club! And we made sure to give it a really fancy sounding title to put on your university applications.
	\end{frame}
	\begin{frame}
		\frametitle{Sign up}
		You can now sign up for Math Club.

		Go to:
		\begin{center}
			\huge
			\url{mackenziemathclub.github.io}
		\end{center}
		And click on \alert{Join the math club}
		\pause

		Once that is done, you can also click on \alert{Apply to be a guest lecturer}. This is a longer form, so we recommend that you do it at home. There is not rush to fill out guest lecturer form, and it is compleely optional.
	\end{frame}
\end{document}
